Paper Figures

### 2019-09-28 PaperFigures.Rmd
separated main figures from supplementary figures

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(text = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=16), axis.text.x = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none") +
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    facet_wrap(~variable)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    theme(text = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5))+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10)+
    labs(x="", y="")
}

@@

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-data.table(read.csv("OG_CD4_bulk_summary_clean.csv"))
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
OG.th1<-read.csv("OG_CD4_OG.TH1_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

@@

tf<-allplot(melt, "TB", "value", all.cols)+    
    labs(y="(%) Total CD4+ T cells")

@@

sm<-allplot(melt, "TB", "value", all.cols) +    
    labs(y="(%) Total CD4+ T cells")

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A' , 'B'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('C', 'D'), nrow=1, label_size = 20)
figure1<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
```

@@

#Figure 2
####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))

one<-allplot(melt, "TB", "value", all.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="(%) Total CD4+ T cells")

@@

two<-allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,8))+
    labs(y="(%) Total CD4+ T cells")

@@

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) Total CD4+ T cells")+coord_cartesian(ylim=c(0,45))+
    labs(title="Healthy Controls")

@@

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A', 'B'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(one, two, labels = c('C', 'D'), nrow=1, label_size = 20)
third_row = cowplot::plot_grid(a, b, c, nrow=1, labels=c('E'), label_size = 20)
figure2 = cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(1,2,2))
```

#Figure 3
####Generic TH1 and TH2 cytokine producing cells are stratified by lineage-specific transcription factors, and CCR4
Amongst TH1 cytokine producing CD4+ T cells, moderate frequencies express the transcription factor T-bet while very low frequencies express GATA3. In contrast, amongst TH2 cytokine producing CD4+ T cells, low frequencies express T-bet while high frequencies express GATA3. Similarly high frequencies of TH2 cytokine producing cells express CCR4 compared to TH1 cytokine producing cells. Both TH1 and TH2 cells have equivalent moderate frequencies of CXCR3 expressing cells. There are no differences by S. mansoni status.

@@

test$subset<-tstrsplit(test$variable, "_")[[1]]
test$subset<-paste(test$subset, "Cytokine+\nCD4+ T Cells", sep=" ")
test$variable<-gsub("TH1_","", test$variable)
test$variable<-gsub("TH2_","", test$variable)
test$variable<-factor(test$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-booleanplot(test, "SM","value", healthy.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="(%) Cytokine+ CD4+ T cells",
         title="HC")

@@

test$subset<-tstrsplit(test$variable, "_")[[1]]
test$subset<-paste(test$subset, "Cytokine+\nCD4+ T Cells", sep=" ")
test$variable<-gsub("TH1_","", test$variable)
test$variable<-gsub("TH2_","", test$variable)
test$variable<-factor(test$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

b<-booleanplot(test, "SM","value", ltbi.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="(%) Cytokine+ CD4+ T cells",
         title="LTBI")

@@

test$subset<-tstrsplit(test$variable, "_")[[1]]
test$subset<-paste(test$subset, "Cytokine+\nCD4+ T Cells", sep=" ")
test$variable<-gsub("TH1_","", test$variable)
test$variable<-gsub("TH2_","", test$variable)
test$variable<-factor(test$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

c<-booleanplot(test, "SM","value", tb.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="(%) Cytokine+ CD4+ T cells",
         title="TB")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(a, b, c, nrow=1, labels=c('B', 'C', 'D'), label_size = 20)
figure3 <- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,4))
```

@@

```{r cytokine, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y = (.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y = (.95*.02))+
    coord_cartesian(ylim=c(0,.02))

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*70))+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(a, b, nrow=1, labels=c('B', 'C'), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, nrow=1, labels=c('D', 'E'), label_size = 20)
figure4 <- cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(1,2,2))
```

@@

####Similar to QFT+, individuals with active TB, co-infected with S. mansoni maintain function Mtb-specific CD4+ T cell cytokine production. There are higher frequencies of TH1/2 cytokine co-producing CD4+ T cells amongst SM+ individuals, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still TH1 cytokine producing cells.
*Again this is where I need an aesthetics opinion*

```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.95*.02))+
    coord_cartesian(ylim=c(0,.02))
```

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))

@@

both<-baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

tbcyt<-cowplot::plot_grid(NULL, a, b, nrow=1, labels=c("A","B", "C"), label_size = 20, rel_widths = c(1.5,1,1))
tbphen<-cowplot::plot_grid(tf, sm, both, nrow=1, labels=c("D","E","F"), label_size = 20)
figure5<-cowplot::plot_grid(tbcyt, tbphen, nrow=2, rel_heights = c(2,3))
```

#Proliferation Assay
#Figure 6
##All Groups Responses to SEB
```{r}
og<-plot_filter(dplyr::filter(OG, Stim=="SEB"))
ogphen<-plot_filter(dplyr::filter(OGPHEN, Stim=="SEB"))

kable(table(og$disease), caption="Total Proliferation")
kable(table(ogphen$disease[!is.na(ogphen$IFNg)]), caption="SEB phenotype")
```

```{r, proliferation and total cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG" = "Proliferation","IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
og<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))

one<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))

two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups)
```

```{r, marker on proliferating, fig.width=15, fig.height=8}
melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

tf<-allplot(melt, "TB", "value", all.cols)+    
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("CXCR3", "CCR4"))

sm<-allplot(melt, "TB", "value", all.cols)

first_row = cowplot::plot_grid(NULL, labels = c('A', 'B'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1.2,2,1), labels=c("B", "C","D"), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, labels=c("E", "F"), nrow=1, label_size = 20)
figure6<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3)
```

@@

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG" = "Proliferation","IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

melt<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
og<-baseplot(melt, "TB", "value", ltbi.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    coord_cartesian(ylim=c(0,3))+
    labs(y="(%) Total CD4+ T cells")

>>>>

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(text = element_text(size=20),
          axis.text.x = element_text(size = 16),
          strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20), 
          axis.text.x = element_text(size=16), 
          strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none") +
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    facet_wrap(~variable)+
    theme(text = element_text(size=20),
            axis.text.x = element_text(size = 16),
            strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20))+
    labs(x="", y="")
}

@@

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-data.table(read.csv("OG_CD4_bulk_summary_clean.csv"))
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OGnope<-read.csv("OG_CD4_noOG_summary_clean.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
OG.th1<-read.csv("OG_CD4_OG.TH1_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

@@

tf<-allplot(melt, "TB", "value", all.cols)+    
    labs(y="(%) Total CD4 T cells")+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10, label.y=25)+
    coord_cartesian(ylim=c(0,30))

@@

sm<-allplot(melt, "TB", "value", all.cols) +    
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="")+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10, label.y=60)

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('B', ''), nrow=1, label_size = 20)
figure1<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
figure1
```

#Figure 1 alt
```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

tf<-allplot(melt, "disease", "value", all.cols)+    
    labs(y="(%) Total CD4 T cells")+
    scale_x_discrete(labels=c("HC\nSM-", "HC\nSM+", 
                              "LTBI\nSM-", "LTBI\nSM+", 
                              "TB\nSM-", "TB\nSM+"))+
    stat_compare_means(comparisons=list(c("HC SM-", "HC SM+")), method = 'wilcox.test', label="p.format", size=6, label.y=.9*30)+
    coord_cartesian(ylim=c(0,30))

sm<-allplot(melt, "disease", "value", all.cols) +    
    labs(y="")+    
    scale_x_discrete(labels=c("HC\nSM-", "HC\nSM+", 
                              "LTBI\nSM-", "LTBI\nSM+", 
                              "TB\nSM-", "TB\nSM+"))+
    stat_compare_means(comparisons=list(c("TB SM-", "TB SM+")), 
                       method = 'wilcox.test', label="p.format", size=6, label.y=.9*65)+
    coord_cartesian(ylim=c(0,65))

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('B', ''), nrow=1, label_size = 20)
figure1alt<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
figure1alt
```

@@

#Figure 2
####Generic cytokine production from CD4 T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=15, fig.height=15}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))

one<-allplot(melt, "TB", "value", all.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Total CD4 T cells")

@@

two<-allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, labeller = cyt_groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    coord_cartesian(ylim=c(0,8))+
    labs(y="")

@@

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) Total CD4 T cells")+coord_cartesian(ylim=c(0,45))+
    labs(title="HC")

@@

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(one, two, labels = c('B', ''), nrow=1, label_size = 20)
third_row = cowplot::plot_grid(a, b, c, nrow=1, labels=c('C'), label_size = 20)
figure2 = cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(1,2,2))
figure2
```

some stats comparing th1 to th2 for reference. 
```{r}
x<-filter(plot_filter(melt), variable!="TH1.2.Freq")
y<-split(x,list(x$SM, x$TB)) 
A<-lapply(y, function(g) wilcox.test(value~variable, g))

pval<-c(A$`SM-.HC`$p.value, A$`SM+.HC`$p.value,
        A$`SM-.LTBI`$p.value, A$`SM+.LTBI`$p.value, 
        A$`SM-.TB`$p.value, A$`SM+.TB`$p.value)
group<-c("HC SM-", "HC SM+", "LTBI SM-", "LTBI SM+", "TB SM-", "TB SM+")
table<-data.frame(cbind(group, pval))
table$pval<-as.numeric(as.character(table$pval))
table$pval[table$pval<.0001]<-"<0.0001"
kable(table, caption="TH1 to TH2")
```

some stats comparing th1 to th1/2 for reference. 
```{r}
x<-filter(plot_filter(melt), variable!="TH2.Freq")
y<-split(x,list(x$SM, x$TB)) 
A<-lapply(y, function(g) wilcox.test(value~variable, g))

pval<-c(A$`SM-.HC`$p.value, A$`SM+.HC`$p.value,
        A$`SM-.LTBI`$p.value, A$`SM+.LTBI`$p.value, 
        A$`SM-.TB`$p.value, A$`SM+.TB`$p.value)
group<-c("HC SM-", "HC SM+", "LTBI SM-", "LTBI SM+", "TB SM-", "TB SM+")
table<-data.frame(cbind(group, pval))
table$pval<-as.numeric(as.character(table$pval))
table$pval[table$pval<.0001]<-"<0.0001"
kable(table, caption="TH1 to TH1/2")
```

#Figure 3
####Generic TH1 and TH2 cytokine producing cells are stratified by lineage-specific transcription factors, and CCR4
Amongst TH1 cytokine producing CD4 T cells, moderate frequencies express the transcription factor T-bet while very low frequencies express GATA3. In contrast, amongst TH2 cytokine producing CD4 T cells, low frequencies express T-bet while high frequencies express GATA3. Similarly high frequencies of TH2 cytokine producing cells express CCR4 compared to TH1 cytokine producing cells. Both TH1 and TH2 cells have equivalent moderate frequencies of CXCR3 expressing cells. There are no differences by S. mansoni status.

@@

test$subset<-tstrsplit(test$variable, "_")[[1]]
test$subset<-paste(test$subset, "Cytokine+\nCD4 T Cells", sep=" ")
test$variable<-gsub("TH1_","", test$variable)
test$variable<-gsub("TH2_","", test$variable)
test$variable<-factor(test$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

a<-booleanplot(test, "SM","value", healthy.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+

    labs(y="(%) Cytokine+ CD4 T cells",
         title="HC")

@@

test$subset<-tstrsplit(test$variable, "_")[[1]]
test$subset<-paste(test$subset, "Cytokine+\nCD4 T Cells", sep=" ")
test$variable<-gsub("TH1_","", test$variable)
test$variable<-gsub("TH2_","", test$variable)
test$variable<-factor(test$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

b<-booleanplot(test, "SM","value", ltbi.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(plot.margin=margin(l=-1,unit="cm"))+
    labs(y="",
         title="LTBI")

@@

test$subset<-tstrsplit(test$variable, "_")[[1]]
test$subset<-paste(test$subset, "Cytokine+\nCD4 T Cells", sep=" ")
test$variable<-gsub("TH1_","", test$variable)
test$variable<-gsub("TH2_","", test$variable)
test$variable<-factor(test$variable, levels=c("T-bet", "GATA3", "CXCR3", "CCR4"))

c<-booleanplot(test, "SM","value", tb.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(plot.margin=margin(l=-1,unit="cm"))+
    labs(y="",
         title="TB")

second_row <- cowplot::plot_grid(a,b,c, nrow=1)
figure3 <- cowplot::plot_grid(NULL, second_row, labels = c('A', 'B'), label_size = 20, ncol=1, rel_heights = c(1.5,4.5))
figure3
```

@@

```{r cytokine, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(comparisons=list(c("SM-","SM+")), method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y = (.90*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4 T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.02))

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific\nTH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,100))+
    labs(y="")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(a, b, tf, sm, nrow=1, labels=c('B', '', 'C', ''), label_size = 20)
figure4opt1 <- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(3,4))
figure4opt1

#first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
#second_row = cowplot::plot_grid(a, b, nrow=1, labels=c('B', 'C'), label_size = 20)
#third_row = cowplot::plot_grid(tf, sm, nrow=1, labels=c('D', 'E'), label_size = 20)
#figure4opt2 <- cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(2.5,4,4))

@@

####Similar to QFT+, individuals with active TB, co-infected with S. mansoni maintain function Mtb-specific CD4 T cell cytokine production. There are higher frequencies of TH1/2 cytokine co-producing CD4 T cells amongst SM+ individuals, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still TH1 cytokine producing cells.
*Again this is where I need an aesthetics opinion*

```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4 T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.02))
```

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(comparisons=list(c("SM-","SM+")), method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific\nTH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,80))

@@

both<-baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = groups)+
    stat_compare_means(comparisons=list(c("SM-","SM+")), method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=.98*13)+
    labs(y="(%) Mtb-Specific\nTH1 Cytokine+ cells")+
    coord_cartesian(ylim=c(0,13))

tbcyt<-cowplot::plot_grid(NULL, a, b, nrow=1, labels=c("A","B", ""), label_size = 20, rel_widths = c(1.5,1,1))
tbphen<-cowplot::plot_grid(tf, sm, both, nrow=1, labels=c("C","","D"), label_size = 20)
figure5<-cowplot::plot_grid(tbcyt, tbphen, nrow=2, rel_heights = c(2,2))
figure5
```

#Proliferation Assay
#Figure 6
##All Groups Responses to SEB
```{r}
groups <- as_labeller(c("OG" = "Proliferation","IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

og<-plot_filter(dplyr::filter(OG, Stim=="SEB"))
part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
seb<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Total CD4 T cells",
         title="SEB")

og<-plot_filter(dplyr::filter(OG, Stim=="PEP", TB %in% c("LTBI", "TB")))
part2<-melt(og, id.vars=c("TB", "SM", "disease"), measure.vars="OG")
pep<-allplot(part2, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nLTBI", "SM- SM+\nTB"))+
    coord_cartesian(ylim=c(0,4))+
    labs(y="(%) Total CD4 T cells",
        title="CFP-10 & ESAT-6")

pep2<-allplot(part2, "disease", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    stat_compare_means(comparisons=list(c("TB SM-", "LTBI SM-"), c("TB SM+", "LTBI SM+")),
                       method="wilcox.test", size=6)+
    coord_cartesian(ylim=c(0,35))+
    labs(y="(%) Total CD4 T cells",
        title="CFP-10 & ESAT-6")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(seb, pep, nrow=1, rel_widths = c(3,2), labels=c("B", "C"), label_size = 20)
figure6a<-cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1.5,3))

second_row = cowplot::plot_grid(seb, pep2, nrow=1, rel_widths = c(3,2), labels=c("B", "C"), label_size = 20)
figure6b<-cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1.5,3))

kable(table(og$disease), caption="Total Proliferation")
figure6a
figure6b
```

@@

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4 T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
one<-baseplot(melt, "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating\nMtb-Specific CD4 T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))
two<-baseplot(melt, "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups)
```
